---
title: "R Notebook"
author: "Gabriela Suardi"
date: "2023-03-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In this file I'll put my notes from John Hopkins' data science course R programming

### *Lesson 1: R console Imput and evaluation*

<- assignment operator : assign a value to a symbol
"#" indicates a comment. Everything on the right of this symbol is ignored
Example:
```{r}
x<- 1     ## nothing printed
x         ## autoprinting occurs
print("The value of x is")     ##explicited printing
print(x)
```
The : operator is used to create interger sequences
Example:
```{r}
x <- 1:20  #this gives us a sequence
x
```
### * Lesson 2: R objects and attributes*
 
 R has five  basic classes of objects:
 -**character**
 -**numeric (real numbers)**
 -**integer**
 - **complex**
 -**logical (true/false)**
 
 The most basic object is a *vector*
 - Everything in R is a object
 -A vector can only contain objects of the *same* class. Example:  a vector containing characters and numerics.
 
 *BUT* the only exception is a **list**, which is represented as a vector but can contain objects of different classes
 Empty vectors can be created with the *vector()* function
 
 The vector function has two basic arguments. The **first argument** is the *class* of the object, so the type of object that you want to have in the vector. And the **second argument** is the *length* of the vector itself.
 
#### Numbers

Numbers in R are generally treated as *numeric objects*
If you explicit wants an integer, you need to use the suffix **L**. Ex: 1L
There's also the special number **inf** which represents infinity.
The **NaN** (not a number) represents an undefined value or a missing value.

### *Lesson 3: Creating vectors*

The c() function (concatenating) can be used to create vectors of an object
```{r}
a <- c(0.5, 0.6) ##number
a
b <- c(TRUE, FALSE) ##logical
d <- c(T, F)   ##logical
e <- c("1", "a", "d", "0.8" ) ##character
f <- 9:29 ##integer
f
g <- c(1+0i, 2+4i) ##complex
g
```
Using the vector function:
```{r}
x <- vector("numeric", length=10)
x
```
When different objects are mixed in a vector, **coercion** occurs so every object is of the same class
When converted to numeric, TRUE is represented by the number 1 and FALSE by 0.

#### Explicit coercion

Objects can be explicit coerced from one class to another
Use of the function as.
```{r}
x <- 0:6
class(x)
as.numeric(x)
as.logical(x) #as a convention, 0 is false and every other number above zero is true
as.character(x)
```

 *Nonsensical* coersions results in *NA*
```{r}
x <- c("a", "b", "c")
as.complex(x)
as.numeric(x)
as.logical(x)

```
 #### Lists
 Lists are a special type of vector that can contain elements from different classes.
```{r}
x <- list(1, "a", TRUE, 1+4i)
x
```
### *Lesson 4: Matrices*

Matrices are vectors with a dimension attribute. The dimension attribute itself is an integer vector of length 2
```{r}
m <- matrix(1:6, nrow = 2, ncol = 3)
m
dim(m)
attributes(m)
dim
```
Matrix can also be created directly from vectors by introducing a dimensional attribute
```{r}
m <- 1:10
dim(m)<- c(2, 5) # I'm assigning an attribute to the vector m
m
```

 Matrices can be created by colunm binding or row binding using cbind() and rbind()
```{r}
x <- 1:3
y <-10:12
cbind(x, y)

rbind(x, y)
```
 




